Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-13 write-ups/PLDI/paper.tex
Edit section on sizing non-persistent kernels

Cooperative kernels enables other \emph{non-persistent} workloads to
access GPU resources without stopping the blocking algorithm
computation entirely. We size these workloads to represent
approximatively the workload required by a system to maintain smooth
screen animations. We repetitively ran a kernel with a controlled
workload and detected from which workload size the screen animation
started to jitter. Given the kernel workload and its scheduling
frequency, we can infer what is the workload and frequency needed by
the system to maintain a smooth animation.

Based on this approach, we measured workloads required by the system
to maintain smooth animations of three types: (\emph{light}) emphasis
of desktop icons under the mouse pointer, (\emph{medium}) window
dragging over the desktop, and (\emph{heavy}) WebGL animations in a
browser. \mytab~\ref{tab:nonpersistentworkload} illustrates our
results. In order to simulate such non-persistent workloads alongside
kernels of blocking algorithms, we use a matrix multiplication kernel
where matrix dimensions are tuned to trigger the relevant execution
duration.

@@

@@

>>>>

Cooperative kernels enables other \emph{non-persistent} workloads to
access GPU resources without stopping the blocking algorithm
computation entirely. We size these workloads to represent
approximatively the workload required by a system to maintain smooth
screen animations.

\paragraph{Experimental setup} \ADComment{Describe the data we are
  gathering.}  We repetitively run a kernel with a controlled workload
and detect from which workload size the screen animation starts to
jitter. Given the kernel workload and its scheduling frequency, we
deduce what is the workload and frequency needed by the system to
maintain a smooth animation. We use this approach to measure required
by the system to maintain smooth animations of three types:
(\emph{light}) emphasis of desktop icons under the mouse pointer,
(\emph{medium}) window dragging over the desktop, and (\emph{heavy})
WebGL animations in a browser.

@@

\paragraph{Results} \ADComment{Discuss the results.}
\mytab~\ref{tab:nonpersistentworkload} illustrates the caracteristics
found for the three types of workloads. For the medium and heavy
workloads, the 40ms period corresponds to an execution every $25^{th}$
of seconds which coincide with the human persistence of vision. The
3ms execution duration of both light and medium configurations may
indicate a lower bound of GPU execution time for system workloads.

@@

In order to simulate non-persistent workloads alongside kernels of
blocking algorithms, we use a matrix multiplication kernel where
matrix dimensions are tuned to trigger the relevant execution
duration.
